A Short Guide to Anyons and Modular Functors

### 2016-09-25 guide.tex
spell check

\begin{abstract}
To the working physicist, anyon theory is meant to describe
certain quasi-particle excitations occuring in two dimensional
topologically ordered systems. 
A typical calculation using this theory will involve operations
such as $\otimes$ to combine anyons, 
$F^{abc}_{d}$ to re-associate such combinations,
and $R^{ab}_c$ to commute or braid these anyons. 
Although there is a powerful string-diagram notation that greatly assists these
manipulations, we still appear to be operating on particles
arranged on a one-dimensional line, algebraically ordered from left to right.
The obvious question is, where is the other dimension?
The topological framework for considering these anyons as truly living in a
two dimensional space is known as a modular functor, or topological
quantum field theory. 
In this work we show how the apparently one-dimensional algebraic anyon theory
is secretly the theory of anyons living in a fully two-dimensional system.
The mathematical literature covering this secret is vast, 
and we try to distil this down into something more manageable.
%While avoiding much of the
%category theoretic jargon found in the mathematical literature.
%To the physicist, anyons are manipulated algebraically, using operations
%such as $\otimes$ to combine, $F^{abc}_{de}$ to re-associate, and $R^{ab}_c$
%to commute or braid. 
%Although there are string-diagram notations that greatly assist these
%manipulations, such calculations still appear to be operating on particles
%arranged in a one-dimensional line, algebraically ordered from left to right.
%The correct notion for considering these anyons as truly living in a
%two dimensional space is known as a modular functor, or topological
%quantum field theory. 
%In this work we show how the apparently one-dimensional algebraic theory
%is secretly a fully-two dimensional theory, while avoiding much of the
%category theoretic jargon found in the mathematical literature.
\end{abstract}

@@

When the above monodromy is constrained to two dimensions
we can no longer deform this process to the identity:
\begin{center}
\includegraphics[]{pic-monodromy2d.pdf}
\end{center}
and so in two dimensions we cannot expect a swap to square to the identity.
To see this more clearly,
we must examine the entire (2+1)-dimensional \emph{world-lines} of these particles.
For an example, here we show the world-lines of three particles undergoing an exchange and then
returning to their original positions:
\begin{center}
\includegraphics[]{pic-braid-worldlines.pdf}
\end{center}
Note that if we allow the particles to move in one extra
dimension then we can untangle these braided world lines.
%The question is, how has the wavefunction of the system
%changed from $t_0$ to $t_1$?
The question is now, what is the group that acts on the
state space from $t_0$ to $t_1$?
Examining the structure of these processes more closely,
we see that we can compose them by sequentially performing
two such braids, one after the other:
\begin{center}
\includegraphics[]{pic-braid-compose.pdf}
\end{center}
And, by ``reversing time'', we can undo the effect of
any braid:
\begin{center}
\includegraphics[]{pic-braid-inverse.pdf}
\end{center}
This shows that these processes do form a group,
known as the \emph{braid group.}
For $n$ particle worldlines we denote this group as $B_n.$
For identicle particles this group acts as symmetries of the
state space:
%Now we would expect to see an action on the statespace $\F_n:$
$$
%    \Phi : B_n \to U(\F_n).
    \F : B_n \to U(V).
$$

What we have given is a topological description of the group $B_n$.
More formally, we can describe these braid world lines as
paths in the \emph{configuration space} of $n$ points.
\newcommand{\Conf}{\mathcal{C}}
\newcommand{\UConf}{\mathcal{UC}}
This space is defined as the product of
a two dimensional space $M$ for each point, minus the subspace where points overlap:
$$
    \Conf_n = \bigl( \prod_{1}^{n} M \bigr) - \Delta, \ \ 
    \Delta = \{(x_1, ..., x_n) | x_i = x_j \ \ \mbox{for some} \ \ i\ne j \}.
$$
Because we are considering identicle particles (so far)
we use the \emph{unlabelled configuration space}
$\UConf_n$ which is the quotient of $\Conf_n$ by the natural action of the
permutation group $S_n:$
%\cggb{I was a bit confused by when we care about
%unlabelled configuration space and when we care about the labelled
%configuration space. What if we have some but not all
%particles identical? Do the two formalisms unify by considering some
%subgroups of the permutation group that preserve particle label or something?}
$$
    \UConf_n = \Conf_n / S_n.
$$
The \emph{geometric braid group} as we have so far informally described it 
can now be rigorously defined as the fundamental group:
$$
    B_n = \pi_1 ( \UConf_n, x )
$$
where $x$ is some reference configuration in $\UConf_n.$
See \cite{Ghrist2014} for further discussion.

%The \emph{braid group} on $n$ strands is denoted $B_n.$
%This group can also be described purely algebraically.
This group also has a purely algebraic description via
generators and relations, as was shown by Artin in 1947, \cite{Artin1947,Birman1974}.
$B_n$ has $n-1$ generators $\sigma_1,..,\sigma_{n-1}$ that satisfy
the following relations:
\begin{align*}
    \sigma_i \sigma_j &= \sigma_j \sigma_i \ \ \ \mbox{for}\ \ |i-j|>1,\\
    \sigma_i \sigma_{i+1} \sigma_i &= \sigma_{i+1} \sigma_i \sigma_{i+1} \ \ \ \mbox{for}\ \ 1\le i \le n-2.
\end{align*}
So these relations are the same as for $S_n$ above, except 
we no longer have the relation $\sigma_i^2 = 1.$

%The easiest way to understand these relations is to consider the
It is easy to see that the geometric braid group satisfies these
relations. Here we show the braids corresponing to the generators $\sigma_i:$
\begin{center}
\includegraphics[]{pic-braid-sigma.pdf}
\end{center}
So that 
$\sigma_i \sigma_j = \sigma_j \sigma_i \ \ \ \mbox{for}\ \ |i-j|>1$
because the two braids are operating on disjoint world-lines.
The second relation is also easy to see:
\begin{center}
\includegraphics[]{pic-braid-YB.pdf}
\end{center}

There is another important geometric representation of
the braid group which is purely two-dimensional.
We pick an $n$-point finite subset $Q_n \subset M$
and consider diffeomorphisms 
%\cggb{why diffeomorphisms and not homeomorphisms?}
$f : M \to M$
that map $Q_n$ to itself.
The \emph{mapping class group} of $M$ relative to $Q_n$
is the set of all such diffeomorphisms up to an equivalence relation $\sim_{\mbox{iso}}$:
$$
    MCG(M, Q_n) = \{ f : M \to M \ \ \mbox{such that}\ \ f(Q_n)=Q_n \} / \sim_{\mbox{iso}}
$$
The equivalence relation $\sim_{\mbox{iso}}$ is called \emph{isotopy}
which allows for any continuous deformation of $f:M\to M$ that
fixes each point in $Q_n.$
Each generator $\sigma_i$ of the braid group is found in $MCG(M, Q_n)$
as a \emph{half-twist} that swaps two points $i, i+1 \in Q_n$:
\begin{center}
\includegraphics[]{pic-halftwist.pdf}
\end{center}
In order to show
the action of
this half-twist we have 
decorated the manifold with
a a checkered pattern,
but there is a more important
object that lives on the manifold
itself.
An \emph{observable} is a simple
closed curve in $M$ that does
not intersect $Q_n.$
Such a closed curve is called an
observable because these will be
associated to measurements
that measure the charge on the
interior of the curve.
The importance of understanding the
braid group as identicle to the mapping class group
is now manifest:
whereas geometric braids act on states
as in a Schr\"{o}dinger picture,
elements of the mapping class group
act on the observables as in
a Heisenberg picture.
\begin{center}
\includegraphics[]{pic-heisenberg.pdf}
\end{center}
This diagram should give the reader some idea as
to why these two definitions of the braid group are
equivelant, but the actual proof of this is somewhat involved.
We refer to \cite{Kassel2010} for an excellent contemporary
reference that fills in these gaps.

@@

All these representations of twists carry
essentially the same information.
In the sequal we will stick
to thinking of particles as boundary
components because this fits well
with the way we are formulating 
observables as simple closed curves in $M$.
%More concretely,
%we augment the configuration space
%with tangent vectors. For each point $x_i$
%in a configuration $(x_1,...,x_n)\in \prod M$ we
%attach a non-zero tangent vector $v_i\in T_{x_i}M.$
%In terms of a mapping class group, we will
%consider not just a manifold $M$ with
%distinguished points $Q_n,$ but a manifold with $n$ disjoint
%boundary componends, or ``holes''.
%Each of these boundary components comes
%with a distinguished point.

At this point in the narative we are 
close to our next destination.
All of these considerations,
of framed or unframed, 
labelled or not,
with possibly different underlying manifolds,
together with observables,
is mean to
be captured by the formalism of a modular functor which we turn to next.

@@

For our purposes a \emph{surface} will be a compact
oriented $2$-dimensional differentiable manifold with boundary. % smooth or topological ?
We will not require surfaces to be connected.
%Each boundary component is oriented (either explicitly or
%otherwise by using the orientation of the manifold)
By a \emph{hole} of $M$ we mean a component of its boundary. % $\partial M$.
Each hole will inherit the manifold orientation,
contain a distinguished \emph{base point},
and be labeled with
%an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
an element from a fixed finite set $\A.$
This is the set of ``anyon labels'', and comes
equiped with a vacuum element $\vac$ 
and an involution $\ \widehat{}\ $ such that $\widehat{\vac}=\vac.$
The involution maps an anyon label to the ``antiparticle'' label.

@@

\subsub{POP decomposition.}
%The reverse process of cutting a surface up
%into pair-of-pants induces a direct sum decomposition
%of the fusion space.
Given a manifold $M$ which is
a disc with two or more holes, 
we show how to present $M$ as the gluing of various
pair-of-pants. Such an arangement will be termed a \emph{POP decomposition.}
(We refer to \cite{Ivanov2001} for more details on this construction,
and \cite{Ghrist2014} for a leisurely description of Morse theory.)
This will yield a decomposition of $\F(M)$ into a direct
sum of fusion spaces of pair-of-pants. % $V_{ab}^c$'s.
%The pair-of-pants can be found using Morse theory.
%We proceed using Morse theory.
%Note that we need $M$ to be a differentiable manifold for
%this to work.
The key idea is to choose a ``height'' function $h:M\to\R$
with some specific properties that allow us to
cut the manifold up along level sets of $h.$
First, we need that critical points of $h$ are isolated.
This is the defining condition for $h$ to be a \emph{Morse function}.
%Choose a Morse function (a generic ``height'' function) $h:M\to\R$
Also, we need that $h$ is constant on $\partial M,$
and the values of $h$ at different critical points are distinct.
Now choose a sequence of non-critical values $a_1<a_2<...<a_n$ in $\R$
such that every interval $[a_{i-1}, a_i]$ 
contains exactly one critical value of $h$ and the image
of $h$ lies within $[a_1, a_n].$
%cuts the manifold into pieces $f^{-1}[a,b]$.
Each component of $h^{-1}([a_{i-1}, a_i])$ is then either
an annulus, a disc, or a pair-of-pants depending on the index of (any)
critical point it contains.
We then re-glue any annuli or discs until there are no more of these
and we have only pair-of-pants.
%\cggb{Is this always possible? What if I have something like
%a cylinder? Then I just get a bunch of annuli however I cut.}
% note: we may still get annuli in a *component* of the pre-image.
\begin{center}
\includegraphics[]{pic-pants.pdf}\ \ \ \ \ \ \ \ \includegraphics[]{pic-pants-1.pdf}
\end{center}

@@

Each standard surface comes with a collection of
\emph{standard POP decompositions}:
these will be POP decompositions where we require each
observable to cross the
equator twice and have counterclockwise orientation.
Up to isotopy, a given standard surface will have only finitely many of these.
On a standard surface with three
interior holes there are two standard POP decompositions,
and one $F$-move that relates these.
On a standard surface with four interior holes there are five 
standard POP decompositions and five $F$-moves that relate these.
In this case the $F$-moves themselves satisfy an equation
that is a trivial consequence of the way we have defined $F$-moves.
%enforced by the axioms of the modular functor.
This is known as the pentagon equation, which we depict as
the following commutative diagram:
\begin{center}
\includegraphics[]{pic-pentagon.pdf}
\end{center}
We are now starting to confuse the notation 
for the topological space $M$ and the fusion space $\F(M).$
Also, each of these $F$-moves is refering to an isomorphism 
that is block decomposed according to the charge sectors 
of the indicated observables.

@@

\subsub{Skeins.}
The preivious figure can be seen as a ``top-down'' view of the
following three dimensional arrangement:
%At this point we can show the relation to skein theory:
\begin{center}
\includegraphics[]{pic-rmove-skein.pdf}
\end{center}
This figure is intended to be topologically
the same as the previous flat figure,
with the addition of a third dimension,
and the $c$ boundary has been shrunk.
Also note thin black lines
connecting the base points.
The black lines do not add any extra structure, they can
be seen as a part of the hexagon cut out by
the green line and boundary components.
But notice this: the black lines are ``framed'' by the green lines. 
These are the ribbons used in skein theory!
Note that all the holes are created equal: there is
no distinction between ``input'' holes and ``output'' holes
(as there is with cobordisms or string diagrams.)

>>>>

\begin{abstract}
To the working physicist, anyon theory is meant to describe
certain quasi-particle excitations occurring in two dimensional
topologically ordered systems. 
A typical calculation using this theory will involve operations
such as $\otimes$ to combine anyons, 
$F^{abc}_{d}$ to re-associate such combinations,
and $R^{ab}_c$ to commute or braid these anyons. 
Although there is a powerful string-diagram notation that greatly assists these
manipulations, we still appear to be operating on particles
arranged on a one-dimensional line, algebraically ordered from left to right.
The obvious question is, where is the other dimension?
The topological framework for considering these anyons as truly living in a
two dimensional space is known as a modular functor, or topological
quantum field theory. 
In this work we show how the apparently one-dimensional algebraic anyon theory
is secretly the theory of anyons living in a fully two-dimensional system.
The mathematical literature covering this secret is vast, 
and we try to distill this down into something more manageable.
%While avoiding much of the
%category theoretic jargon found in the mathematical literature.
%To the physicist, anyons are manipulated algebraically, using operations
%such as $\otimes$ to combine, $F^{abc}_{de}$ to re-associate, and $R^{ab}_c$
%to commute or braid. 
%Although there are string-diagram notations that greatly assist these
%manipulations, such calculations still appear to be operating on particles
%arranged in a one-dimensional line, algebraically ordered from left to right.
%The correct notion for considering these anyons as truly living in a
%two dimensional space is known as a modular functor, or topological
%quantum field theory. 
%In this work we show how the apparently one-dimensional algebraic theory
%is secretly a fully-two dimensional theory, while avoiding much of the
%category theoretic jargon found in the mathematical literature.
\end{abstract}

@@

When the above monodromy is constrained to two dimensions
we can no longer deform this process to the identity:
\begin{center}
\includegraphics[]{pic-monodromy2d.pdf}
\end{center}
and so in two dimensions we cannot expect a swap to square to the identity.
To see this more clearly,
we must examine the entire (2+1)-dimensional \emph{world-lines} of these particles.
For an example, here we show the world-lines of three particles undergoing an exchange and then
returning to their original positions:
\begin{center}
\includegraphics[]{pic-braid-worldlines.pdf}
\end{center}
Note that if we allow the particles to move in one extra
dimension then we can untangle these braided world lines.
%The question is, how has the wavefunction of the system
%changed from $t_0$ to $t_1$?
The question is now, what is the group that acts on the
state space from $t_0$ to $t_1$?
Examining the structure of these processes more closely,
we see that we can compose them by sequentially performing
two such braids, one after the other:
\begin{center}
\includegraphics[]{pic-braid-compose.pdf}
\end{center}
And, by ``reversing time'', we can undo the effect of
any braid:
\begin{center}
\includegraphics[]{pic-braid-inverse.pdf}
\end{center}
This shows that these processes do form a group,
known as the \emph{braid group.}
For $n$ particle worldlines we denote this group as $B_n.$
For identical particles this group acts as symmetries of the
state space:
%Now we would expect to see an action on the statespace $\F_n:$
$$
%    \Phi : B_n \to U(\F_n).
    \F : B_n \to U(V).
$$

What we have given is a topological description of the group $B_n$.
More formally, we can describe these braid world lines as
paths in the \emph{configuration space} of $n$ points.
\newcommand{\Conf}{\mathcal{C}}
\newcommand{\UConf}{\mathcal{UC}}
This space is defined as the product of
a two dimensional space $M$ for each point, minus the subspace where points overlap:
$$
    \Conf_n = \bigl( \prod_{1}^{n} M \bigr) - \Delta, \ \ 
    \Delta = \{(x_1, ..., x_n) | x_i = x_j \ \ \mbox{for some} \ \ i\ne j \}.
$$
Because we are considering identical particles (so far)
we use the \emph{unlabelled configuration space}
$\UConf_n$ which is the quotient of $\Conf_n$ by the natural action of the
permutation group $S_n:$
%\cggb{I was a bit confused by when we care about
%unlabelled configuration space and when we care about the labelled
%configuration space. What if we have some but not all
%particles identical? Do the two formalisms unify by considering some
%subgroups of the permutation group that preserve particle label or something?}
$$
    \UConf_n = \Conf_n / S_n.
$$
The \emph{geometric braid group} as we have so far informally described it 
can now be rigorously defined as the fundamental group:
$$
    B_n = \pi_1 ( \UConf_n, x )
$$
where $x$ is some reference configuration in $\UConf_n.$
See \cite{Ghrist2014} for further discussion.

%The \emph{braid group} on $n$ strands is denoted $B_n.$
%This group can also be described purely algebraically.
This group also has a purely algebraic description via
generators and relations, as was shown by Artin in 1947, \cite{Artin1947,Birman1974}.
In this description, 
$B_n$ is generated by $n-1$ elements $\sigma_1,..,\sigma_{n-1}$ that satisfy
the following relations:
\begin{align*}
    \sigma_i \sigma_j &= \sigma_j \sigma_i \ \ \ \mbox{for}\ \ |i-j|>1,\\
    \sigma_i \sigma_{i+1} \sigma_i &= \sigma_{i+1} \sigma_i \sigma_{i+1} \ \ \ \mbox{for}\ \ 1\le i \le n-2.
\end{align*}
These relations are the same as for $S_n$ above, except 
we do not require $\sigma_i^2 = 1.$

%The easiest way to understand these relations is to consider the
It is easy to see that the geometric braid group satisfies these
relations. Here we show the braids corresponding to the generators $\sigma_i:$
\begin{center}
\includegraphics[]{pic-braid-sigma.pdf}
\end{center}
So that 
$\sigma_i \sigma_j = \sigma_j \sigma_i \ \ \ \mbox{for}\ \ |i-j|>1$
because the two braids are operating on disjoint world-lines.
The second relation is also easy to see:
\begin{center}
\includegraphics[]{pic-braid-YB.pdf}
\end{center}

There is another important geometric representation of
the braid group which is purely two-dimensional.
We pick an $n$-point finite subset $Q_n \subset M$
and consider diffeomorphisms 
%\cggb{why diffeomorphisms and not homeomorphisms?}
$f : M \to M$
that map $Q_n$ to itself.
The \emph{mapping class group} of $M$ relative to $Q_n$
is the set of all such diffeomorphisms up to an equivalence relation $\sim_{\mbox{iso}}$:
$$
    MCG(M, Q_n) = \{ f : M \to M \ \ \mbox{such that}\ \ f(Q_n)=Q_n \} / \sim_{\mbox{iso}}
$$
The equivalence relation $\sim_{\mbox{iso}}$ is called \emph{isotopy}
which allows for any continuous deformation of $f:M\to M$ that
fixes each point in $Q_n.$
Each generator $\sigma_i$ of the braid group is found in $MCG(M, Q_n)$
as a \emph{half-twist} that swaps two points $i, i+1 \in Q_n$:
\begin{center}
\includegraphics[]{pic-halftwist.pdf}
\end{center}
In order to show
the action of
this half-twist we have 
decorated the manifold with
a a checkered pattern,
but there is a more important
object that lives on the manifold
itself.
An \emph{observable} is a simple
closed curve in $M$ that does
not intersect $Q_n.$
Such a closed curve is called an
observable because these will be
associated to measurements
that measure the charge on the
interior of the curve.
The importance of understanding the
braid group as identical to the mapping class group
is now manifest:
whereas geometric braids act on states
as in a Schr\"{o}dinger picture,
elements of the mapping class group
act on the observables as in
a Heisenberg picture.
\begin{center}
\includegraphics[]{pic-heisenberg.pdf}
\end{center}
This diagram should give the reader some idea as
to why these two definitions of the braid group are
equivalent, but the actual proof of this is somewhat involved.
We refer to \cite{Kassel2010} for an excellent contemporary
reference that fills in these gaps.

@@

All these representations of twists carry
essentially the same information.
In the sequel we will stick
to thinking of particles as boundary
components because this fits well
with the way we are formulating 
observables as simple closed curves in $M$.
%More concretely,
%we augment the configuration space
%with tangent vectors. For each point $x_i$
%in a configuration $(x_1,...,x_n)\in \prod M$ we
%attach a non-zero tangent vector $v_i\in T_{x_i}M.$
%In terms of a mapping class group, we will
%consider not just a manifold $M$ with
%distinguished points $Q_n,$ but a manifold with $n$ disjoint
%boundary componends, or ``holes''.
%Each of these boundary components comes
%with a distinguished point.

At this point in the narrative we are 
close to our next destination.
All of these considerations,
of framed or unframed, 
labelled or not,
with possibly different underlying manifolds,
together with observables,
is mean to
be captured by the formalism of a modular functor which we turn to next.

@@

For our purposes a \emph{surface} will be a compact
oriented $2$-dimensional differentiable manifold with boundary. % smooth or topological ?
We will not require surfaces to be connected.
%Each boundary component is oriented (either explicitly or
%otherwise by using the orientation of the manifold)
By a \emph{hole} of $M$ we mean a component of its boundary. % $\partial M$.
Each hole will inherit the manifold orientation,
contain a distinguished \emph{base point},
and be labeled with
%an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
an element from a fixed finite set $\A.$
This is the set of ``anyon labels'', and comes
equipped with a vacuum element $\vac$ 
and an involution $\ \widehat{}\ $ such that $\widehat{\vac}=\vac.$
The involution maps an anyon label to the ``antiparticle'' label.

@@

\subsub{POP decomposition.}
%The reverse process of cutting a surface up
%into pair-of-pants induces a direct sum decomposition
%of the fusion space.
Given a manifold $M$ which is
a disc with two or more holes, 
we show how to present $M$ as the gluing of various
pair-of-pants. Such an arrangement will be termed a \emph{POP decomposition.}
(We refer to \cite{Ivanov2001} for more details on this construction,
and \cite{Ghrist2014} for a leisurely description of Morse theory.)
This will yield a decomposition of $\F(M)$ into a direct
sum of fusion spaces of pair-of-pants. % $V_{ab}^c$'s.
%The pair-of-pants can be found using Morse theory.
%We proceed using Morse theory.
%Note that we need $M$ to be a differentiable manifold for
%this to work.
The key idea is to choose a ``height'' function $h:M\to\R$
with some specific properties that allow us to
cut the manifold up along level sets of $h.$
First, we need that critical points of $h$ are isolated.
This is the defining condition for $h$ to be a \emph{Morse function}.
%Choose a Morse function (a generic ``height'' function) $h:M\to\R$
Also, we need that $h$ is constant on $\partial M,$
and the values of $h$ at different critical points are distinct.
Now choose a sequence of non-critical values $a_1<a_2<...<a_n$ in $\R$
such that every interval $[a_{i-1}, a_i]$ 
contains exactly one critical value of $h$ and the image
of $h$ lies within $[a_1, a_n].$
%cuts the manifold into pieces $f^{-1}[a,b]$.
Each component of $h^{-1}([a_{i-1}, a_i])$ is then either
an annulus, a disc, or a pair-of-pants depending on the index of (any)
critical point it contains.
We then re-glue any annuli or discs until there are no more of these
and we have only pair-of-pants.
%\cggb{Is this always possible? What if I have something like
%a cylinder? Then I just get a bunch of annuli however I cut.}
% note: we may still get annuli in a *component* of the pre-image.
\begin{center}
\includegraphics[]{pic-pants.pdf}\ \ \ \ \ \ \ \ \includegraphics[]{pic-pants-1.pdf}
\end{center}

@@

Each standard surface comes with a collection of
\emph{standard POP decompositions}:
these will be POP decompositions where we require each
observable to cross the
equator twice and have counterclockwise orientation.
Up to isotopy, a given standard surface will have only finitely many of these.
On a standard surface with three
interior holes there are two standard POP decompositions,
and one $F$-move that relates these.
On a standard surface with four interior holes there are five 
standard POP decompositions and five $F$-moves that relate these.
In this case the $F$-moves themselves satisfy an equation
that is a trivial consequence of the way we have defined $F$-moves.
%enforced by the axioms of the modular functor.
This is known as the pentagon equation, which we depict as
the following commutative diagram:
\begin{center}
\includegraphics[]{pic-pentagon.pdf}
\end{center}
We are now starting to confuse the notation 
for the topological space $M$ and the fusion space $\F(M).$
Also, each of these $F$-moves is referring to an isomorphism 
that is block decomposed according to the charge sectors 
of the indicated observables.

@@

\subsub{Skeins.}
The previous figure can be seen as a ``top-down'' view of the
following three dimensional arrangement:
%At this point we can show the relation to skein theory:
\begin{center}
\includegraphics[]{pic-rmove-skein.pdf}
\end{center}
This figure is intended to be topologically
the same as the previous flat figure,
with the addition of a third dimension,
and the $c$ boundary has been shrunk.
Also note thin black lines
connecting the base points.
The black lines do not add any extra structure, they can
be seen as a part of the hexagon cut out by
the green line and boundary components.
But notice this: the black lines are ``framed'' by the green lines. 
These are the ribbons used in skein theory!
Note that all the holes are created equal: there is
no distinction between ``input'' holes and ``output'' holes
(as there is with cobordisms or string diagrams.)
